Regularising Lotka--Volterra Interaction Matrices by Species Grouping

### 2021-10-08 article.rnw
Correct spelling.

The experiment also included a number of other vials that were excluded for various reasons.
The original authors' study was on parasitism, so the experiments also included a parasitised treatment.
That is irrelevant to this study, so was excluded.
Vials with a single founding pair were excluded from this study and the original authors' due to an Allee effect that the Lotka--Volterra cannot accomodate.
Lastly, an additional set of vials were raised in colder temperatures, but were excluded from this study and the original authors' as the resulting emergence was too low to analyse.

@@

I determined the phylogenic relationships between the six study species, by examination of the literature, in order to compare these to the groupings generated by the models.
No attempt was made to determine absolute phylogenetic distances, for sufficient data was not available on all six species for this purpose.
Rather, I only determined relative times of evolutionary divergence sufficient to form a binary phylogenetic tree.

@@

	\caption{%
		Coclassification matrices of the Lotka--Volterra competitive effects and responses of the six studied \emph{Drosophila} species, weighted by AIC weights.
		The cell for a pair of species represents the probability that the best grouping, as determined by the AIC weights of the grouped models, places those two species in the same group.
		\Cref{fig:coclassification-cols} represents the grouping of species' competetive effects upon other species (columns of the interaction matrix), while \cref{fig:coclassification-rows} represents the grouping of species' responses to competition (rows of the interaction matrix).
	}
	\label{fig:coclassification}
\end{figure}

>>>>

The experiment also included a number of other vials that were excluded for various reasons.
The original authors' study was on parasitism, so the experiments also included a parasitised treatment.
That is irrelevant to this study, so was excluded.
Vials with a single founding pair were excluded from this study and the original authors' due to an Allee effect that the Lotka--Volterra cannot accommodate.
Lastly, an additional set of vials were raised in colder temperatures, but were excluded from this study and the original authors' as the resulting emergence was too low to analyse.

@@

I determined the phylogenetic relationships between the six study species, by examination of the literature, in order to compare these to the groupings generated by the models.
No attempt was made to determine absolute phylogenetic distances, for sufficient data was not available on all six species for this purpose.
Rather, I only determined relative times of evolutionary divergence sufficient to form a binary phylogenetic tree.

@@

	\caption{%
		Coclassification matrices of the Lotka--Volterra competitive effects and responses of the six studied \emph{Drosophila} species, weighted by AIC weights.
		The cell for a pair of species represents the probability that the best grouping, as determined by the AIC weights of the grouped models, places those two species in the same group.
		\Cref{fig:coclassification-cols} represents the grouping of species' competitive effects upon other species (columns of the interaction matrix), while \cref{fig:coclassification-rows} represents the grouping of species' responses to competition (rows of the interaction matrix).
	}
	\label{fig:coclassification}
\end{figure}
